---
title: "Step 2. Statistical tests"
author: "Erica Chavez Santos"
date: "2022-12-19"
output:
  pdf_document: default
  html_document: default
---


```{r clear.workspace, eval=FALSE, echo=FALSE, include =FALSE}
#-----clear workspace-----
# Clear the environment without clearing knitr

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
    suppressWarnings(
        lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
               detach, character.only=TRUE, unload=TRUE, force=TRUE)
        )
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("~/Documents/Git/EBP Eval Outcomes")

# Load the other packages, installing as needed.
pacman::p_load(readr, dplyr, tidyr, lubridate, table1, stringr, ggplot2, kableExtra)


# read in data
df_outcomes <- read_csv("cleaned_data.csv") 

depression6 <- read_csv("phq9_6_data.csv") 
depression10 <- read_csv("phq9_10_data.csv") 

## filter out enrollees so we only have completers for tests
df_outcomes <- df_outcomes %>% 
  filter(completers != "Enrollees") # N = 578

df_depression6 <- depression6 %>% 
  filter(completers != "Enrollees") # N = 173

df_depression10 <- depression10 %>% 
  filter(completers != "Enrollees") # N = 80

CDSMP <- df_outcomes %>% 
  filter(q10 == "CDSMP")

CPSMP <- df_outcomes %>% 
  filter(q10 == "CPSMP")

DSMP <- df_outcomes %>% 
  filter(q10 == "DSMP")

EnhanceFitness <- df_outcomes %>% 
  filter(q10 == "EnhanceFitness")

WalkEase <- df_outcomes %>% 
  filter(q10 == "Walk with Ease")

```

### Statistical tests
#### Completers only

#### Loneliness
```{r loneliness, echo=FALSE}
loneliness <- t.test(df_outcomes$loneliness[df_outcomes$pre_post=="Pre"],df_outcomes$loneliness[df_outcomes$pre_post=="Post"], paired = TRUE)

loneliness

fisher.test(df_outcomes$loneliness[df_outcomes$pre_post=="Pre"],df_outcomes$loneliness[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)

```

#### Social isolation
```{r social isolation, echo=FALSE}
social_isolation <- t.test(df_outcomes$soc_isolation[df_outcomes$pre_post=="Pre"],df_outcomes$soc_isolation[df_outcomes$pre_post=="Post"], paired = TRUE)

social_isolation


fisher.test(df_outcomes$soc_isolation[df_outcomes$pre_post=="Pre"],df_outcomes$soc_isolation[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety
```{r anxiety, echo=FALSE}
anxiety <- t.test(df_outcomes$anxiety[df_outcomes$pre_post=="Pre"],df_outcomes$anxiety[df_outcomes$pre_post=="Post"], paired = TRUE)
anxiety

fisher.test(df_outcomes$anxiety[df_outcomes$pre_post=="Pre"],df_outcomes$anxiety[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression 
```{r depression, echo=FALSE}
depression <- t.test(df_outcomes$depression[df_outcomes$pre_post=="Pre"],df_outcomes$depression[df_outcomes$pre_post=="Post"], paired = TRUE)
depression

fisher.test(df_outcomes$depression[df_outcomes$pre_post=="Pre"],df_outcomes$depression[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression > 6
```{r depression 6, echo =FALSE}
table(depression6$depression, depression6$pre_post)
depression6 <- t.test(depression6$depression[depression6$pre_post=="Pre"],depression6$depression[depression6$pre_post=="Post"], paired = TRUE)

depression6

fisher.test(df_depression6$depression[df_depression6$pre_post=="Pre"],df_depression6$depression[df_depression6$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression 10
```{r depression 10, echo = FALSE}
table(depression10$depression, depression10$pre_post)
depression10 <- t.test(depression10$depression[depression10$pre_post=="Pre"],depression10$depression[depression10$pre_post=="Post"], paired = TRUE)

depression10

fisher.test(df_depression10$depression[df_depression10$pre_post=="Pre"],df_depression10$depression[df_depression10$pre_post=="Post"], simulate.p.value=TRUE)

```


#### Physical activity
```{r physcial activity, echo=FALSE}
phys_activity <- t.test(df_outcomes$phys_activity[df_outcomes$pre_post=="Pre"],df_outcomes$phys_activity[df_outcomes$pre_post=="Post"], paired = TRUE)
phys_activity

fisher.test(df_outcomes$phys_activity[df_outcomes$pre_post=="Pre"],df_outcomes$phys_activity[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days
```{r physical activity days, echo=FALSE}
Days <- t.test(df_outcomes$pa1[df_outcomes$pre_post=="Pre"],df_outcomes$pa1[df_outcomes$pre_post=="Post"], paired = TRUE)
Days

fisher.test(df_outcomes$pa1[df_outcomes$pre_post=="Pre"],df_outcomes$pa1[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes
```{r physical activity minutes, echo=FALSE}
Minutes <- t.test(df_outcomes$pa2[df_outcomes$pre_post=="Pre"],df_outcomes$pa2[df_outcomes$pre_post=="Post"], paired = TRUE)
Minutes

fisher.test(df_outcomes$pa2[df_outcomes$pre_post=="Pre"],df_outcomes$pa2[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs
```{r social needs, echo=FALSE}
soc_needs <- t.test(df_outcomes$social_needs[df_outcomes$pre_post=="Pre"],df_outcomes$social_needs[df_outcomes$pre_post=="Post"], paired = TRUE)
soc_needs

fisher.test(df_outcomes$social_needs[df_outcomes$pre_post=="Pre"],df_outcomes$social_needs[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy
```{r self efficacy, echo=FALSE}
self_efficacy <- t.test(df_outcomes$self_efficacy[df_outcomes$pre_post=="Pre"],df_outcomes$self_efficacy[df_outcomes$pre_post=="Post"], paired = TRUE)
self_efficacy

fisher.test(df_outcomes$self_efficacy[df_outcomes$pre_post=="Pre"],df_outcomes$self_efficacy[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference
```{r pain interference, echo=FALSE}
pain_interference <- t.test(df_outcomes$pain_interference[df_outcomes$pre_post=="Pre"],df_outcomes$pain_interference[df_outcomes$pre_post=="Post"], paired = TRUE)
pain_interference

fisher.test(df_outcomes$pain_interference[df_outcomes$pre_post=="Pre"],df_outcomes$pain_interference[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes
```{r diabetes, echo=FALSE}
diabetes <- t.test(df_outcomes$diabetes[df_outcomes$pre_post=="Pre"],df_outcomes$diabetes[df_outcomes$pre_post=="Post"], paired = TRUE)
diabetes

fisher.test(df_outcomes$diabetes[df_outcomes$pre_post=="Pre"],df_outcomes$diabetes[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health
```{r health, echo=FALSE}
health <- t.test(df_outcomes$health[df_outcomes$pre_post=="Pre"],df_outcomes$health[df_outcomes$pre_post=="Post"], paired = TRUE)
health

fisher.test(df_outcomes$health[df_outcomes$pre_post=="Pre"],df_outcomes$health[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Fatigue
```{r fatigue, echo=FALSE}
fatigue <- t.test(df_outcomes$fatigue[df_outcomes$pre_post=="Pre"],df_outcomes$fatigue[df_outcomes$pre_post=="Post"], paired = TRUE)
fatigue

fisher.test(df_outcomes$fatigue[df_outcomes$pre_post=="Pre"],df_outcomes$fatigue[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain
```{r pain, echo=FALSE}
pain <- t.test(df_outcomes$pain[df_outcomes$pre_post=="Pre"],df_outcomes$pain[df_outcomes$pre_post=="Post"], paired = TRUE)
pain

fisher.test(df_outcomes$pain[df_outcomes$pre_post=="Pre"],df_outcomes$pain[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep
```{r sleep, echo=FALSE}
sleep <- t.test(df_outcomes$sleep[df_outcomes$pre_post=="Pre"],df_outcomes$sleep[df_outcomes$pre_post=="Post"], paired = TRUE)
sleep

fisher.test(df_outcomes$sleep[df_outcomes$pre_post=="Pre"],df_outcomes$sleep[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3
```{r tech3, echo=FALSE}
tech3 <- t.test(df_outcomes$tech3[df_outcomes$pre_post=="Pre"],df_outcomes$tech3[df_outcomes$pre_post=="Post"], paired = TRUE)

tech3

fisher.test(df_outcomes$tech3[df_outcomes$pre_post=="Pre"],df_outcomes$tech3[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4
```{r tech4, echo=FALSE}
tech4 <- t.test(df_outcomes$tech4[df_outcomes$pre_post=="Pre"],df_outcomes$tech4[df_outcomes$pre_post=="Post"], paired = TRUE)

tech4

fisher.test(df_outcomes$tech4[df_outcomes$pre_post=="Pre"],df_outcomes$tech4[df_outcomes$pre_post=="Post"], simulate.p.value=TRUE)
```

### Tests by program (t-tests and Fshter's, except EnhanceFitness)
##### Note: EnhanceFitness I only ran Fisher's test because sample is so small N = 24

## CDSMP
#### Loneliness (CDSMP)
```{r loneliness CDSMP, echo=FALSE}
t.test(CDSMP$loneliness[CDSMP$pre_post=="Pre"],CDSMP$loneliness[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$loneliness[CDSMP$pre_post=="Pre"],CDSMP$loneliness[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)

```

#### Social isolation (CDSMP)
```{r social isolation CDSMP, echo=FALSE}

t.test(CDSMP$soc_isolation[CDSMP$pre_post=="Pre"],CDSMP$soc_isolation[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$soc_isolation[CDSMP$pre_post=="Pre"],CDSMP$soc_isolation[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety (CDSMP)
```{r anxiety CDSMP, echo=FALSE}
t.test(CDSMP$anxiety[CDSMP$pre_post=="Pre"],CDSMP$anxiety[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$anxiety[CDSMP$pre_post=="Pre"],CDSMP$anxiety[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Depression (CDSMP)
```{r depression CDSMP, echo=FALSE}
t.test(CDSMP$depression[CDSMP$pre_post=="Pre"],CDSMP$depression[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$depression[CDSMP$pre_post=="Pre"],CDSMP$depression[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity (CDSMP)
```{r physcial activity CDSMP, echo=FALSE}
t.test(CDSMP$phys_activity[CDSMP$pre_post=="Pre"],CDSMP$phys_activity[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$phys_activity[CDSMP$pre_post=="Pre"],CDSMP$phys_activity[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days (CDSMP)
```{r physical activity days CDSMP, echo=FALSE}
t.test(CDSMP$pa1[CDSMP$pre_post=="Pre"],CDSMP$pa1[CDSMP$pre_post=="Post"], paired = TRUE)
Days

fisher.test(CDSMP$pa1[CDSMP$pre_post=="Pre"],CDSMP$pa1[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes (CDSMP)
```{r physical activity minutes CDSMP, echo=FALSE}
t.test(CDSMP$pa2[CDSMP$pre_post=="Pre"],CDSMP$pa2[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$pa2[CDSMP$pre_post=="Pre"],CDSMP$pa2[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs (CDSMP)
```{r social needs CDSMP, echo=FALSE}
t.test(CDSMP$social_needs[CDSMP$pre_post=="Pre"],CDSMP$social_needs[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$social_needs[CDSMP$pre_post=="Pre"],CDSMP$social_needs[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy (CDSMP)
```{r self efficacy CDSMP, echo=FALSE}
t.test(CDSMP$self_efficacy[CDSMP$pre_post=="Pre"],CDSMP$self_efficacy[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$self_efficacy[CDSMP$pre_post=="Pre"],CDSMP$self_efficacy[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference (CDSMP) 
##### Note: No observations, t-test wouldn't run
```{r pain interference CDSMP, echo=FALSE}
# table(CDSMP$pain_interference)
# t.test(CDSMP$pain_interference[CDSMP$pre_post=="Pre"],CDSMP$pain_interference[CDSMP$pre_post=="Post"], paired = TRUE)
# 
# 
# fisher.test(CDSMP$pain_interference[CDSMP$pre_post=="Pre"],CDSMP$pain_interference[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes (CDSMP)
##### Note: No observations, t-test wouldn't run
```{r diabetes CDSMP, echo=FALSE}
# table(df_outcomes$diabetes, df_outcomes$q10)
# t.test(CDSMP$diabetes[CDSMP$pre_post=="Pre"],CDSMP$diabetes[CDSMP$pre_post=="Post"], paired = TRUE)
# 
# 
# fisher.test(CDSMP$diabetes[CDSMP$pre_post=="Pre"],CDSMPs$diabetes[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health (CDSMP)
```{r health CDSMP, echo=FALSE}
t.test(CDSMP$health[CDSMP$pre_post=="Pre"],CDSMP$health[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$health[CDSMP$pre_post=="Pre"],CDSMP$health[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Fatigue (CDSMP)
```{r fatigue CDSMP, echo=FALSE}

t.test(CDSMP$fatigue[CDSMP$pre_post=="Pre"],CDSMP$fatigue[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$fatigue[CDSMP$pre_post=="Pre"],CDSMP$fatigue[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain (CDSMP)
```{r pain CDSMP, echo=FALSE}
t.test(CDSMP$pain[CDSMP$pre_post=="Pre"],CDSMP$pain[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$pain[CDSMP$pre_post=="Pre"],CDSMP$pain[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep (CDSMP)
```{r sleep CDSMP, echo=FALSE}
t.test(CDSMP$sleep[CDSMP$pre_post=="Pre"],CDSMP$sleep[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$sleep[CDSMP$pre_post=="Pre"],CDSMP$sleep[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3 (CDSMP)
```{r tech3 CDSMP, echo=FALSE}
t.test(CDSMP$tech3[CDSMP$pre_post=="Pre"],CDSMP$tech3[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$tech3[CDSMP$pre_post=="Pre"],CDSMP$tech3[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4 (CDSMP)
```{r tech4 CDSMP, echo=FALSE}
t.test(CDSMP$tech4[CDSMP$pre_post=="Pre"],CDSMP$tech4[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$tech4[CDSMP$pre_post=="Pre"],CDSMP$tech4[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


## CPSMP
#### Loneliness (CPSMP)
```{r loneliness CPSMP, echo=FALSE}
t.test(CDSMP$loneliness[CDSMP$pre_post=="Pre"],CDSMP$loneliness[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$loneliness[CDSMP$pre_post=="Pre"],CDSMP$loneliness[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social isolation (CPSMP)
```{r social isolation CPSMP, echo=FALSE}

t.test(CDSMP$soc_isolation[CDSMP$pre_post=="Pre"],CDSMP$soc_isolation[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$soc_isolation[CDSMP$pre_post=="Pre"],CDSMP$soc_isolation[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety (CPSMP)
```{r anxiety CPSMP, echo=FALSE}
t.test(CDSMP$anxiety[CDSMP$pre_post=="Pre"],CDSMP$anxiety[CDSMP$pre_post=="Post"], paired = TRUE)


fisher.test(CDSMP$anxiety[CDSMP$pre_post=="Pre"],CDSMP$anxiety[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression (CPSMP)
```{r depression CPSMP, echo=FALSE}
t.test(CDSMP$depression[CDSMP$pre_post=="Pre"],CDSMP$depression[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$depression[CDSMP$pre_post=="Pre"],CDSMP$depression[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity (CPSMP)
```{r physcial activity CPSMP, echo=FALSE}
t.test(CDSMP$phys_activity[CDSMP$pre_post=="Pre"],CDSMP$phys_activity[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$phys_activity[CDSMP$pre_post=="Pre"],CDSMP$phys_activity[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days (CPSMP)
```{r physical activity days CPSMP, echo=FALSE}
t.test(CDSMP$pa1[CDSMP$pre_post=="Pre"],CDSMP$pa1[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$pa1[CDSMP$pre_post=="Pre"],CDSMP$pa1[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes (CPSMP)
```{r physical activity minutes CPSMP, echo=FALSE}
t.test(CDSMP$pa2[CDSMP$pre_post=="Pre"],CDSMP$pa2[CDSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CDSMP$pa2[CDSMP$pre_post=="Pre"],CDSMP$pa2[CDSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs (CPSMP)
```{r social needs CPSMP, echo=FALSE}
t.test(CPSMP$social_needs[CPSMP$pre_post=="Pre"],CPSMP$social_needs[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$social_needs[CPSMP$pre_post=="Pre"],CPSMP$social_needs[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy (CPSMP)
##### Note: No observations, t-tests won't run
```{r self efficacy CPSMP, echo=FALSE}
# t.test(CPSMP$self_efficacy[CPSMP$pre_post=="Pre"],CPSMP$self_efficacy[CPSMP$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(CPSMP$self_efficacy[CPSMP$pre_post=="Pre"],CPSMP$self_efficacy[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference (CPSMP)
```{r pain interference CPSMP, echo=FALSE}
t.test(CPSMP$pain_interference[CPSMP$pre_post=="Pre"],CPSMP$pain_interference[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$pain_interference[CPSMP$pre_post=="Pre"],CPSMP$pain_interference[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes (CPSMP)
##### Note: No observations, t-tests won't run
```{r diabetes CPSMP, echo=FALSE}
# t.test(CPSMP$diabetes[CPSMP$pre_post=="Pre"],CPSMP$diabetes[CPSMP$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(CPSMP$diabetes[CPSMP$pre_post=="Pre"],CPSMP$diabetes[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health (CPSMP)
```{r health CPSMP, echo=FALSE}
t.test(CPSMP$health[CPSMP$pre_post=="Pre"],CPSMP$health[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$health[CPSMP$pre_post=="Pre"],CPSMP$health[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Fatigue (CPSMP)
```{r fatigue CPSMP, echo=FALSE}
t.test(CPSMP$fatigue[CPSMP$pre_post=="Pre"],CPSMP$fatigue[CPSMP$pre_post=="Post"], paired = TRUE)
fatigue

fisher.test(CPSMP$fatigue[CPSMP$pre_post=="Pre"],CPSMP$fatigue[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain (CPSMP)
```{r pain CPSMP, echo=FALSE}
t.test(CPSMP$pain[CPSMP$pre_post=="Pre"],CPSMP$pain[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$pain[CPSMP$pre_post=="Pre"],CPSMP$pain[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep (CPSMP)
```{r sleep CPSMP, echo=FALSE}
t.test(CPSMP$sleep[CPSMP$pre_post=="Pre"],CPSMP$sleep[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$sleep[CPSMP$pre_post=="Pre"],CPSMP$sleep[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3 (CPSMP)
```{r tech3 CPSMP, echo=FALSE}
t.test(CPSMP$tech3[CPSMP$pre_post=="Pre"],CPSMP$tech3[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$tech3[CPSMP$pre_post=="Pre"],CPSMP$tech3[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4 (CPSMP)
```{r tech4 CPSMP, echo=FALSE}
t.test(CPSMP$tech4[CPSMP$pre_post=="Pre"],CPSMP$tech4[CPSMP$pre_post=="Post"], paired = TRUE)

fisher.test(CPSMP$tech4[CPSMP$pre_post=="Pre"],CPSMP$tech4[CPSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


## DSMP
#### Loneliness (DSMP)
```{r loneliness DSMP, echo=FALSE}
t.test(DSMP$loneliness[DSMP$pre_post=="Pre"],DSMP$loneliness[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$loneliness[DSMP$pre_post=="Pre"],DSMP$loneliness[DSMP$pre_post=="Post"], simulate.p.value=TRUE)

```

#### Social isolation (DSMP)
```{r social isolation DSMP, echo=FALSE}
t.test(DSMP$soc_isolation[DSMP$pre_post=="Pre"],DSMP$soc_isolation[DSMP$pre_post=="Post"], paired = TRUE)


fisher.test(DSMP$soc_isolation[DSMP$pre_post=="Pre"],DSMP$soc_isolation[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety (DSMP)
```{r anxiety DSMP, echo=FALSE}
t.test(DSMP$anxiety[DSMP$pre_post=="Pre"],DSMP$anxiety[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$anxiety[DSMP$pre_post=="Pre"],DSMP$anxiety[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression (DSMP)
```{r depression DSMP, echo=FALSE}
t.test(DSMP$depression[DSMP$pre_post=="Pre"],DSMP$depression[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$depression[DSMP$pre_post=="Pre"],DSMP$depression[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity (DSMP)
```{r physcial activity DSMP, echo=FALSE}
t.test(DSMP$phys_activity[DSMP$pre_post=="Pre"],DSMP$phys_activity[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$phys_activity[DSMP$pre_post=="Pre"],DSMP$phys_activity[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days (DSMP)
```{r physical activity days DSMP, echo=FALSE}
t.test(DSMP$pa1[DSMP$pre_post=="Pre"],DSMP$pa1[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$pa1[DSMP$pre_post=="Pre"],DSMP$pa1[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes (DSMP)
```{r physical activity minutes DSMP, echo=FALSE}
t.test(DSMP$pa2[DSMP$pre_post=="Pre"],DSMP$pa2[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$pa2[DSMP$pre_post=="Pre"],DSMP$pa2[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs (DSMP)
```{r social needs DSMP, echo=FALSE}
t.test(DSMP$social_needs[DSMP$pre_post=="Pre"],DSMP$social_needs[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$social_needs[DSMP$pre_post=="Pre"],DSMP$social_needs[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy (DSMP)
##### Note: N= 1 observations, t-tests won't run
```{r self efficacy DSMP, echo=FALSE}
# t.test(DSMP$self_efficacy[DSMP$pre_post=="Pre"],DSMP$self_efficacy[DSMP$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(DSMP$self_efficacy[DSMP$pre_post=="Pre"],DSMP$self_efficacy[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference (DSMP)
##### Note: No observations, t-tests won't run
```{r pain interference DSMP, echo=FALSE}
# t.test(DSMP$pain_interference[DSMP$pre_post=="Pre"],DSMP$pain_interference[DSMP$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(DSMP$pain_interference[DSMP$pre_post=="Pre"],DSMP$pain_interference[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes (DSMP)
```{r diabetes DSMP, echo=FALSE}
t.test(DSMP$diabetes[DSMP$pre_post=="Pre"],DSMP$diabetes[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$diabetes[DSMP$pre_post=="Pre"],DSMP$diabetes[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health (DSMP)
```{r health DSMP, echo=FALSE}
t.test(DSMP$health[DSMP$pre_post=="Pre"],DSMP$health[DSMP$pre_post=="Post"], paired = TRUE)


fisher.test(DSMP$health[DSMP$pre_post=="Pre"],DSMP$health[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Fatigue (DSMP)
```{r fatigue DSMP, echo=FALSE}
t.test(DSMP$fatigue[DSMP$pre_post=="Pre"],DSMP$fatigue[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$fatigue[DSMP$pre_post=="Pre"],DSMP$fatigue[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain (DSMP)
```{r pain DSMP, echo=FALSE}
t.test(DSMP$pain[DSMP$pre_post=="Pre"],DSMP$pain[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$pain[DSMP$pre_post=="Pre"],DSMP$pain[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep (DSMP)
```{r sleep DSMP, echo=FALSE}
t.test(DSMP$sleep[DSMP$pre_post=="Pre"],DSMP$sleep[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$sleep[DSMP$pre_post=="Pre"],DSMP$sleep[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3 (DSMP)
```{r tech3 DSMP, echo=FALSE}
t.test(DSMP$tech3[DSMP$pre_post=="Pre"],DSMP$tech3[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$tech3[DSMP$pre_post=="Pre"],DSMP$tech3[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4 (DSMP)
```{r tech4 DSMP, echo=FALSE}
t.test(DSMP$tech4[DSMP$pre_post=="Pre"],DSMP$tech4[DSMP$pre_post=="Post"], paired = TRUE)

fisher.test(DSMP$tech4[DSMP$pre_post=="Pre"],DSMP$tech4[DSMP$pre_post=="Post"], simulate.p.value=TRUE)
```

## Enhance Fitness
#### Loneliness (Enhance Fitness)
```{r loneliness Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$loneliness[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$loneliness[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$loneliness[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$loneliness[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)

```


#### Social isolation (Enhance Fitness)
```{r social isolation Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$soc_isolation[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$soc_isolation[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$soc_isolation[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$soc_isolation[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety (Enhance Fitness)
```{r anxiety Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$anxiety[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$anxiety[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$anxiety[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$anxiety[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression (Enhance Fitness)
```{r depression Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$depression[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$depression[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$depression[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$depression[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity (Enhance Fitness)
```{r physcial activity Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$phys_activity[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$phys_activity[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$phys_activity[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$phys_activity[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days (Enhance Fitness)
```{r physical activity days Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$pa1[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pa1[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$pa1[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pa1[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes (Enhance Fitness)
```{r physical activity minutes Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$pa2[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pa2[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$pa2[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pa2[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs (Enhance Fitness)
```{r social needs Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$social_needs[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$social_needs[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$social_needs[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$social_needs[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy (Enhance Fitness)
##### Note: No observations, t-tests won't run
```{r self efficacy Enhance Fitness, echo=FALSE}
# t.test(EnhanceFitness$self_efficacy[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$self_efficacy[EnhanceFitness$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(EnhanceFitness$self_efficacy[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$self_efficacy[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference (Enhance Fitness)
##### Note: No observations, t-tests won't run
```{r pain interference Enhance Fitness, echo=FALSE}
# t.test(EnhanceFitness$pain_interference[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pain_interference[EnhanceFitness$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(EnhanceFitness$pain_interference[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pain_interference[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes (Enhance Fitness)
##### Note: No observations, t-tests won't run
```{r diabetes Enhance Fitness, echo=FALSE}
# t.test(EnhanceFitness$diabetes[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$diabetes[EnhanceFitness$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(EnhanceFitness$diabetes[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$diabetes[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health (Enhance Fitness)
```{r health Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$health[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$health[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$health[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$health[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Fatigue (Enhance Fitness)
```{r fatigue Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$fatigue[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$fatigue[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$fatigue[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$fatigue[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain (Enhance Fitness)
```{r pain Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$pain[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pain[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$pain[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$pain[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep (Enhance Fitness)
```{r sleep Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$sleep[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$sleep[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$sleep[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$sleep[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3 (Enhance Fitness)
```{r tech3 Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$tech3[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$tech3[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$tech3[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$tech3[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4 (Enhance Fitness)
```{r tech4 Enhance Fitness, echo=FALSE}
t.test(EnhanceFitness$tech4[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$tech4[EnhanceFitness$pre_post=="Post"], paired = TRUE)

fisher.test(EnhanceFitness$tech4[EnhanceFitness$pre_post=="Pre"],EnhanceFitness$tech4[EnhanceFitness$pre_post=="Post"], simulate.p.value=TRUE)
```

## Walk with Ease
#### Loneliness (Walk with Ease)
```{r loneliness Walk with Ease, echo=FALSE}
t.test(WalkEase$loneliness[WalkEase$pre_post=="Pre"],WalkEase$loneliness[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$loneliness[WalkEase$pre_post=="Pre"],WalkEase$loneliness[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)

```

#### Social isolation (Walk with Ease)
```{r social isolation Walk with Ease, echo=FALSE}
t.test(WalkEase$soc_isolation[WalkEase$pre_post=="Pre"],WalkEase$soc_isolation[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$soc_isolation[WalkEase$pre_post=="Pre"],WalkEase$soc_isolation[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Anxiety (Walk with Ease)
```{r anxiety Walk with Ease, echo=FALSE}
t.test(WalkEase$anxiety[WalkEase$pre_post=="Pre"],WalkEase$anxiety[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$anxiety[WalkEase$pre_post=="Pre"],WalkEase$anxiety[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Depression (Walk with Ease)
```{r depression Walk with Ease, echo=FALSE}
t.test(WalkEase$depression[WalkEase$pre_post=="Pre"],WalkEase$depression[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$depression[WalkEase$pre_post=="Pre"],WalkEase$depression[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity (Walk with Ease)
```{r physcial activity Walk with Ease, echo=FALSE}
t.test(WalkEase$phys_activity[WalkEase$pre_post=="Pre"],WalkEase$phys_activity[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$phys_activity[WalkEase$pre_post=="Pre"],WalkEase$phys_activity[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Physical activity - # of days (Walk with Ease)
```{r physical activity days Walk with Ease, echo=FALSE}
t.test(WalkEase$pa1[WalkEase$pre_post=="Pre"],WalkEase$pa1[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$pa1[WalkEase$pre_post=="Pre"],WalkEase$pa1[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Physical activity - # of minutes (Walk with Ease)
```{r physical activity minutes Walk with Ease, echo=FALSE}
t.test(WalkEase$pa2[WalkEase$pre_post=="Pre"],WalkEase$pa2[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$pa2[WalkEase$pre_post=="Pre"],WalkEase$pa2[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Social needs (Walk with Ease)
```{r social needs Walk with Ease, echo=FALSE}
t.test(WalkEase$social_needs[WalkEase$pre_post=="Pre"],WalkEase$social_needs[WalkEase$pre_post=="Post"], paired = TRUE)


fisher.test(WalkEase$social_needs[WalkEase$pre_post=="Pre"],WalkEase$social_needs[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-efficacy (Walk with Ease)
##### Note: No observations, t-tests won't run
```{r self efficacy Walk with Ease, echo=FALSE}
# t.test(WalkEase$self_efficacy[WalkEase$pre_post=="Pre"],WalkEase$self_efficacy[WalkEase$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(WalkEase$self_efficacy[WalkEase$pre_post=="Pre"],WalkEase$self_efficacy[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```


#### Pain interference (Walk with Ease)
##### Note: No observations, t-tests won't run
```{r pain interference Walk with Ease, echo=FALSE}
# t.test(WalkEase$pain_interference[WalkEase$pre_post=="Pre"],WalkEase$pain_interference[WalkEase$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(WalkEase$pain_interference[WalkEase$pre_post=="Pre"],WalkEase$pain_interference[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Diabetes (Walk with Ease)
##### Note: No observations, t-tests won't run
```{r diabetes Walk with Ease, echo=FALSE}
# t.test(WalkEase$diabetes[WalkEase$pre_post=="Pre"],WalkEase$diabetes[WalkEase$pre_post=="Post"], paired = TRUE)
# 
# fisher.test(WalkEase$diabetes[WalkEase$pre_post=="Pre"],WalkEase$diabetes[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Self-rated health (Walk with Ease)
```{r health Walk with Ease, echo=FALSE}
t.test(WalkEase$health[WalkEase$pre_post=="Pre"],WalkEase$health[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$health[WalkEase$pre_post=="Pre"],WalkEase$health[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Fatigue (Walk with Ease)
```{r fatigue Walk with Ease, echo=FALSE}
t.test(WalkEase$fatigue[WalkEase$pre_post=="Pre"],WalkEase$fatigue[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$fatigue[WalkEase$pre_post=="Pre"],WalkEase$fatigue[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Pain (Walk with Ease)
```{r pain Walk with Ease, echo=FALSE}
t.test(WalkEase$pain[WalkEase$pre_post=="Pre"],WalkEase$pain[WalkEase$pre_post=="Post"], paired = TRUE)


fisher.test(WalkEase$pain[WalkEase$pre_post=="Pre"],WalkEase$pain[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Sleep (Walk with Ease)
```{r sleep Walk with Ease, echo=FALSE}
t.test(WalkEase$sleep[WalkEase$pre_post=="Pre"],WalkEase$sleep[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$sleep[WalkEase$pre_post=="Pre"],WalkEase$sleep[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech3 (Walk with Ease)
```{r tech3 Walk with Ease, echo=FALSE}
t.test(WalkEase$tech3[WalkEase$pre_post=="Pre"],WalkEase$tech3[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$tech3[WalkEase$pre_post=="Pre"],WalkEase$tech3[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```

#### Tech4 (Walk with Ease)
```{r tech4 Walk with Ease, echo=FALSE}
t.test(WalkEase$tech4[WalkEase$pre_post=="Pre"],WalkEase$tech4[WalkEase$pre_post=="Post"], paired = TRUE)

fisher.test(WalkEase$tech4[WalkEase$pre_post=="Pre"],WalkEase$tech4[WalkEase$pre_post=="Post"], simulate.p.value=TRUE)
```


